# Reproducible Research: Peer Assessment 1

## Loading and preprocessing the data
```{r}
suppressPackageStartupMessages(require(data.table))
data <- fread('activity.csv')
```

## Histogram of Steps
```{r}
suppressPackageStartupMessages(require(ggplot2))
ggplot(data) + geom_histogram(aes(steps), binwidth=30) + labs(x='Steps')
```

## What are the mean and median number of steps taken per day?
```{r}
mean(data$steps, na.rm=T)
median(data$steps, na.rm=T)
```

## What is the average daily activity pattern?
```{r}
suppressPackageStartupMessages(require(dplyr))
time <- data %>% group_by(interval) %>% summarise(steps=mean(steps, na.rm=T))
ggplot(time, aes(interval, steps)) + geom_line() + labs(x='Time', y='Steps')
highest <- time[which.max(steps),]$interval
```
Time interval `r highest` has the most steps

## Imputing missing values
```{r}
num_missing <- sum(is.na(data))
```
There are `r num_missing` missing values

### Imputing missing values with the average value of steps for that day
```{r}
imputed_data <- copy(data)
impute_step <- Vectorize(function(inter, steps) {
	if(is.na(steps)) {
		return(mean(data[interval == inter,]$steps, na.rm=T))
	} else {
		return(steps)
	}
})
imputed_data[,steps:=impute_step(interval, steps)]
```

## Histogram of Imputed Steps
```{r}
ggplot(imputed_data) + geom_histogram(aes(steps), binwidth=30) + labs(x='Steps')
```

## Mean and median of imputed data
```{r}
mean(imputed_data$steps)
median(imputed_data$steps)
```
These values are the same as before NA values were filled in.

However, the number of steps has increased by `r (sum(imputed_data$steps) - sum(data$steps, na.rm=T)) / dim(data)[1]` per day

## Are there differences in activity patterns between weekdays and weekends?
```{r}
suppressPackageStartupMessages(require(lubridate))
imputed_data[,date:=ymd(date)]
imputed_data[,weekend:=as.factor(ifelse(
		weekdays(date) == 'Sunday' | weekdays(date) == 'Saturday',
		'weekend',
		'weekday'
	))]
imputed_summary <- data.frame(imputed_data) %>% regroup(list('weekend', 'interval')) %>% summarise(steps=mean(steps))
ggplot(imputed_summary, aes(interval, steps)) + geom_line() + facet_wrap(~weekend, ncol=1) + labs(x='Time', y='Steps')
```

